---
title: "DataAnalysis"
output: 
  html_document:
    keep_md: true
---

```{r}
library(tidyverse)
library(readr)
library(tidyr)
```

# Load and Clean Data 
```{r}
Artists<-read.csv("~/Desktop/describing_your_data/Data/Data_Sets/artandfemWiki.csv")
Athletes<- read.csv("~/Desktop/describing_your_data/Data/Data_Sets/athletesWiki.csv")
Politicians <- read.csv("~/Desktop/describing_your_data/Data/Data_Sets/politicsWiki.csv")
Scientists <- read.csv("~/Desktop/describing_your_data/Data/Data_Sets/ScientistsWiki.csv")

# Add a column to each for their group 
Artists$type<-"Artists"
Athletes$type<-"Athletes"
Politicians$type <-"Politicians"
Scientists$type<-"Scientists"

# Add a column for Athletes and Politicans, so have consistent number of variables 
Athletes$New <- "N/A"
Politicians$New <- "N/A"

# Combine into one data set 
all_data<- rbind(Artists,Athletes,Politicians,Scientists)
```

# Descriptive Statistics 

**Number of articles per group** 

Table 1. Articles per Group, broken down by articles started by the groups and those edited by them. 

```{r}
all_data %>%
  count(type)

all_data %>%
  group_by(type)%>%
  count(New)
```

**Length Statistics**
```{r}
all_data%>%
  group_by(type)%>%
  summarise(average=mean(length), median=median(length), max=max(length), min=min(length))

library(ggridges)

figure1<-ggplot(all_data)+
  geom_density_ridges(aes(x=log(length), y=type, fill=type), quantile_lines=TRUE, quantiles=2, show.legend=FALSE)+ 
  ggtitle("Figure 1. Length of articles, by group")+ 
  scale_fill_manual(values=c("#254181","#138d75","#a2d9ce","#72b2f5"))+
  ylab(" ")+
  xlab("log of character count")


figure2<-ggplot()+
  geom_boxplot(data=Artists, aes(x=type, y=log(length), fill=New))+
  geom_boxplot(data=Scientists, aes(x=type, y=log(length), fill=New))+
  ggtitle("Figure 2. Length of Newly Created and Edited Articles for Intervention Groups ")+
  ylab("log of character count")+
  xlab(" ")+
  scale_fill_manual(name = " ", labels = c("Existing Articles", "Newly Created"), values=c("#673990","#e7dbf2"))+
  theme_minimal()

figure1
figure2

length_New<-all_data%>%
  group_by(type, New)%>%
  summarise(median(length), mean(length))

length_New
```

**Wikilinks Statistics** 

```{r}
Artists_Net<-read.csv("~/Desktop/describing_your_data/Data/Wikilinks_Networks/ArtistsNet.csv")
Athletes_Net<- read.csv("~/Desktop/describing_your_data/Data/Wikilinks_Networks/AthletesNet.csv")
Politicians_Net<- read.csv("~/Desktop/describing_your_data/Data/Wikilinks_Networks/PoliticiansNet.csv")
Scientists_Net<- read.csv("~/Desktop/describing_your_data/Data/Wikilinks_Networks/ScientistsNet.csv")

Artists_Neta<-Artists_Net %>%
  group_by(Source)%>%
  summarise(num_of_links=n_distinct(Destination)) 

Athletes_Neta<-Athletes_Net %>%
  group_by(Source)%>%
  summarise(num_of_links=n_distinct(Destination))

Politicians_Neta<- Politicians_Net %>%
  group_by(Source)%>%
  summarise(num_of_links=n_distinct(Destination))
  
Scientists_Neta<- Scientists_Net %>%
  group_by(Source)%>%
  summarise(num_of_links=n_distinct(Destination))


mean(Artists_Neta$num_of_links)
mean(Athletes_Neta$num_of_links)
mean(Politicians_Neta$num_of_links)
mean(Scientists_Neta$num_of_links)


median(Artists_Neta$num_of_links)
median(Athletes_Neta$num_of_links)
median(Politicians_Neta$num_of_links)
median(Scientists_Neta$num_of_links)


colnames(Artists_Neta)[colnames(Artists_Neta) == 'Source'] <- 'title'
colnames(Athletes_Neta)[colnames(Athletes_Neta) == 'Source'] <- 'title'
colnames(Politicians_Neta)[colnames(Politicians_Neta) == 'Source'] <- 'title'
colnames(Scientists_Neta)[colnames(Scientists_Neta) == 'Source'] <- 'title'

all_nets <- rbind(Artists_Neta, Athletes_Neta, Politicians_Neta, Scientists_Neta)
all_data_net<- merge(all_data, all_nets, by="title")

figure3<-ggplot(all_data_net, aes(x=length, y=num_of_links, color=type))+
  geom_point()+
  geom_smooth(aes(method="lm", se=FALSE))+
  scale_color_manual(values=c("#254181","#138d75","#a2d9ce","#72b2f5"))+
  ggtitle("Figure 3. Relationship of Wikilinks and length, per group ")+
  xlab("Character count")+
  ylab("Count of Wikilinks")+
  theme_minimal()

figure3
```

**Infobox Statistics** 
```{r}
infobox_report<-all_data%>%
  group_by(type)%>%
  summarise(total=length(infobox),no_info=length(infobox)-length(unique(infobox)))

infobox_report

infobox_report_long<-gather(infobox_report, Info, N, total:no_info, factor_key=TRUE)
infobox_report_long


figure4<-ggplot(data=infobox_report_long)+
  geom_col(aes(x=type,y=N, fill=Info), position="dodge", show.legend=TRUE)+
  scale_fill_manual(values=c("#673990", "#d2b4de"), labels=c("Total Articles", "No InfoBox"))+
  ggtitle("Figure 4. Proportion of Articles Without Infoboxes within each group")+
  ylab("Number of Articles")+
  xlab(" ")+
  theme_minimal()
      
figure4
```


**Average number of editors**
```{r}
editors<-all_data%>%
  group_by(type) %>%
  summarise(average=mean(editorcount), median=median(editorcount), max=max(editorcount), min=min(editorcount))

editors
```

**Average number of pageviewss**
```{r}
pageviews<-all_data%>%
  group_by(type) %>%
  summarise(average=mean(aveviews), median=median(aveviews), max=max(aveviews), min=min(aveviews))
```

**Pageview and Editor Plots** 
```{r}
figure5<-ggplot(data=all_data) +
  geom_boxplot(aes(x=type, y=log(aveviews), fill=type), show.legend=FALSE)+
  scale_fill_manual(values=c("#254181","#138d75","#a2d9ce","#72b2f5"))+
  theme_minimal()+
  xlab("")+
  ylab("Count of daily pageviews, logarithmic scale")+
  ggtitle("Figure 5. Median Daily Page Views by Group")


figure6<-ggplot(data=all_data)+
  geom_boxplot(aes(x=type, y=log(editorcount), fill=type), show.legend=FALSE)+
  theme_minimal()+
  scale_fill_manual(values=c("#254181","#138d75","#a2d9ce","#72b2f5"))+
  xlab("")+
  ylab("Editor count, logarithmic scale")+
  ggtitle("Figure 6. Median Editors by Group")

figure5
figure6
```

**Pageviews and Editor Count for New and Existing Articles**
```{r}
figure7<-ggplot()+
  geom_boxplot(data=Artists, aes(x=type, y=log(aveviews), fill=New))+
  geom_boxplot(data=Scientists, aes(x=type, y=log(aveviews), fill=New))+
  ggtitle("Figure 7. Pageviews of Newly Created and Edited Articles \n for Intervention Groups ")+
  ylab("log of pageviews")+
  xlab(" ")+
  scale_fill_manual(name = " ", labels = c("Existing Articles", "Newly Created"), values=c("#673990","#e7dbf2"))+
  theme_minimal()


figure8<- ggplot()+
  geom_boxplot(data=Artists, aes(x=type, y=log(editorcount), fill=New))+
  geom_boxplot(data=Scientists, aes(x=type, y=log(editorcount), fill=New))+
  ggtitle("Figure 8. Editor Count of Newly Created and Edited Articles \n for Intervention Groups ")+
  ylab("log of editor count")+
  xlab(" ")+
  scale_fill_manual(name = " ", labels = c("Existing Articles", "Newly Created"), values=c("#673990","#e7dbf2"))+
  theme_minimal()

figure7
figure8

figure9<-ggplot(all_data)+
  geom_point(aes(x=editorcount, y=length, col=type))+
  geom_smooth(aes(x=editorcount, y=length, col=type, method="lm", se=FALSE))+
  scale_color_manual(values=c("#254181","#138d75","#a2d9ce","#72b2f5"))+
  theme_minimal()+
  ylab("length of article")+
  xlab("editorcount")+
  ggtitle("Figure 9. Relationship between number of editors and length of article")

  
figure9
```



