---
title: "OSF Preregistration: Wikilink Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
# By default, the code chunks are hidden for brevity. Set the echo argument to TRUE for blocks you want to share the code in the output for. 
knitr::opts_chunk$set(echo = F)
```

```{r packages and data }
# Load packages and data to be clear from the start
```

## Study Information

### 1.	Title 

Feminist Interventions on Wikipedia: From Collaboration to Content 


### 2.	Authorship

<!--
List authors and affiliations as applicable. Placing a number or letter in upward arrows, (e.g. ^2^) creates a superscript
--> 

Isabelle Langrock^1^ 

^1^ University of Pennsylvania 

### 3. Description

<!--
Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions. 
Example: Though there is strong evidence to suggest that sugar affects taste preferences, the effect has never been demonstrated in brownies. Therefore, we will measure taste preference for four different levels of sugar concentration in a standard brownie recipe to determine if the effect exists in this pastry. 
More info: The description should be no longer than the length of an abstract. It can give some context for the proposed study, but great detail is not needed here for your preregistration. 
-->

With over 5 million entries in the English language edition alone, Wikipedia is the world’s largest collaborative endeavor. However, equally well documented is Wikipedia’s gender problem: not only do women participate as editors at significantly lower levels than men, even when compared with gender gaps in other technological pursuits, but biographies of women are often incomplete, poorly edited, or even remain unwritten. Scholars from STS, Communication, Media Studies, and Computational Social Science have examined the persistence and vastness of these gaps and even made suggestions for improvement, yet few have examined the effects of the initiatives attempting to remedy the disparity. This project examines how feminist movements reconceptulize collaboration as a process of sharing values and motivations rather than a system that allows many people to participate, as described in Wikipedia's norms. Establishing these two forms of collaboration, this project also looks at how they impact the structure of the content that is produced by examing Wikipedia's algorithmic assessment of article quality and the wikilink structure, both of which have impacts beyond the site, between female biographical articles edited by the movements and other groups that have no interventions: female politicans, athletes, and academics. The data includes a corpus of training materials and mission statements from the two movements and Wikipedia for qualitative thematic analysis of how collaboration is thought about by all three populations. Additional data for computational assesment includes the biographical articles and their revision history from the movement's dashboards tracking edits as well as other identified biographical articles for comparison. 

This research project serves as an example of the combined socio-techinical effects of any digital collaborative endevor on the product. Furthermore, the focus on feminist interventions on a platform with a prevalent gender gap refocuses attention away from a deficeit based model that looks at what women are not doing and towards a framework that suggests how sociotechnical processes can be hostile, and become more open, to marginalizes populations.  

### 4.	Hypotheses

<!-- 
List specific, concise, and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here. If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis. 
Example: If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar. 
-->

1. **Wikilinks**  
Do the articles edited by the feminist movements (500 Women Scientists and Art+Feminism) link to each other more than other biographical articles grouped by occupation and more than to be expected by random chance? 

_Given the motivations of collaboration of the two groups to make their histories visible and placing emphasis on the value of gathering together to edit Wikipedia and learn from each other, I expect to find a more dense network within the scientist and artist groups than the other groups._ 
 
## Design Plan

<!-- 
In this section, you will be asked to describe the overall design of your study. Remember that this research plan is designed to register a single study, so if you have multiple experimental designs, please complete a separate preregistration. 
-->

### 5.	Study Type 

<!-- 
Delete all that do not apply.
-->

- Observational Study - Data is collected from study subjects that are not randomly assigned to a treatment. This includes surveys, natural experiments, and regression discontinuity designs.


### 6.	Blinding

<!-- 
Blinding describes who is aware of the experimental manipulations within a study. Delete all that do not apply. 
-->

- No blinding is involved in this study.


### 7.	Is there any additional blinding in this study?

<!-- 
Describe any additional blinding procedures that were not covered by the options above. 
-->

There are no blinding procedures in this study.

### 8.	Study design

<!-- 
Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.
Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. 
More info: This question has a variety of possible answers. The key is for a researcher to be as detailed as is necessary given the specifics of their design. Be careful to determine if every parameter has been specified in the description of the study design. There may be some overlap between this question and the following questions. That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information. For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information. 
-->

This study will build a citation network of nodes with nodes as the biographical articles and edges representing the wikilinks from one article to another. Network density and modularity will be compared across the two "treatment" groups of articles pulled from the movement's edits dashboards (see below) and groups of other biographies sorted by profession. 


### 9.	Randomization

<!-- 
If you are doing a randomized study, how will you randomize, and at what level?
Example: We will use block randomization, where each participant will be randomly assigned to one of the four equally sized, predetermined blocks. The random number list used to create these four blocks will be created using the web applications available at http://random.org. 
More info: Typical randomization techniques include: simple, block, stratified, and adaptive covariate randomization. If randomization is required for the study, the method should be specified here, not simply the source of random numbers.
-->

Randomization is not applicable. 

## Sampling Plan 

<!-- 
In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study. 
-->

The sample for this research project is pulled from the recorded edits on the two movement's dashboards, a tool provided by Wikipedia for groups to track their edits, then reduced to only the biographical content. All articles edited that are not biographical (i.e. about theories, concepts, objects, and/or places) are ommitted from the sample. Groups of similiar size are selected for the "Control" groups using the names included on Wikipedia lists for each profession/group. Lists were collected by searching Wikipedia for "Female X profession" and then selecting names from each list available. Duplicates were removed. 

### 10. Existing data

<!-- 
Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact the COS if you have questions about how to answer this question (prereg@cos.io). 
Delete all that do not apply. 
-->


- Registration prior to analysis of the data: As of the date of submission, the data exist and you have accessed it, though no analysis has been conducted related to the research plan (including calculation of summary statistics). A common situation for this scenario when a large dataset exists that is used for many different studies over time, or when a data set is randomly split into a sample for exploratory analyses, and the other section of data is reserved for later confirmatory data analysis.



### 11.	Explanation of existing data

<!-- 
If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data. This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study. 
Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point. 
More info: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point. 
-->

The data used in this study is publically available as it is public commons content from Wikipedia. Additionally, research conducted on the movements has led to a familiarity with Wikipedia edits and individual biogrpahies. However I have not analyzed the large data set nor have I assembled the data for the "control" conditions prior to making the hypotheses. 


### 12.	Data collection procedures

<!-- 
Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that donÍt include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use. 
Example: Participants will be recruited through advertisements at local pastry shops. Participants will be paid $10 for agreeing to participate (raised to $30 if our sample size is not reached within 15 days of beginning recruitment). Participants must be at least 18 years old and be able to eat the ingredients of the pastries.
More information: The answer to this question requires a specific set of instructions so that another person could repeat the data collection procedures and recreate the study population. Alternatively, if the study population would be unable to be reproduced because it relies on a specific set of circumstances unlikely to be recreated (e.g., a community of people from a specific time and location), the criteria and methods for creating the group and the rationale for this unique set of subjects should be clear. 
--> 

Data is collected by assembling a list of biographical pages from the movements' edit dashboards and Wikipedia lists of "Women in X" where x is another proffesional/occuptaional category, matching the movements' respective emphasises on scientists and artists. Data about each article will be then collected using the Wikipedia API, including a list of wikilinks for each article. 


### 13.	Sample size

<!-- 
Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis?
Example: Our target sample size is 280 participants. We will attempt to recruit up to 320, assuming that not all will complete the total task. 
More information: For some studies, this will simply be the number of samples or the number of clusters. For others, this could be an expected range, minimum, or maximum number. 
-->

Sample size is determined by the number of biographical pages Art+Feminsim and 500 Women Scientists have claimed to edited through the WikiMedia dashboard tracking tool. The other professional groups was gathered through the lists. Duplicates and nonbiographical information is then removed. 



### 14. Sample size rationale 

<!-- 
This could include a power analysis or an arbitrary constraint such as time, money, or personnel.
Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. 
More information: This gives you an opportunity to specifically state how the sample size will be determined. A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications. If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to “fill in the blanks.” Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints. 
-->

Sample size was determined by how many pages the movement's have edited. 

### 15. Stopping rule 

<!-- 
If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection. 
Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week. We will post 20 new slots each week if, on that Friday night, we are below 320 participants. 
More information: You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules. Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified. If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained. 
-->

Not applicable. 

## Variables 

<!-- 
In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so. 
-->

### 16. Manipulated variables

<!-- 
Describe all variables you plan to manipulate and the levels or treatment arms of each variable. This is not applicable to any observational study. 
Example: We manipulated the percentage of sugar by mass added to brownies. The four levels of this categorical variable are: 15%, 20%, 25%, or 40% cane sugar by mass. 
More information: For any experimental manipulation, you should give a precise definition of each manipulated variable. This must include a precise description of the levels at which each variable will be set, or a specific definition for each categorical treatment. For example, “loud or quiet,” should instead give either a precise decibel level or a means of recreating each level. 'Presence/absence' or 'positive/negative' is an acceptable description if the variable is precisely described.
-->

Not applicable.  

### 17. Measured variables 

<!-- 
Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.
Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat. We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being ‘not at all’, 7 being ‘a great deal’) and ‘How good did the brownie taste’ (on a scale of 1-7, 1 being ‘very bad’, 7 being ‘very good’). 
More information: Observational studies and meta-analyses will include only measured variables. As with the previous questions, the answers here must be precise. For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague. Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'
-->

 - Network density: measuring how well connected (dense) each network, seperated by occupation, is. This is a ratio of the number of edges observed and the number of edges possible in the network. 

 - Network modularity: modularity is a form of community detection, detailing how many groups (of nodes more highly connected to each other than others in the network) are in the network. While density tells us about the whole network, modularity is able to give us a better picture of how the network is dispersed. 

### 18. Indices 

<!-- 
If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.
Example: We will take the mean of the two questions above to create a single measure of ‘brownie enjoyment.’ 
More information: If you are using multiple pieces of data to construct a single variable, how will this occur? Both the data that are included and the formula or weights for each measure must be specified. Standard summary statistics, such as “means” do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined. For example, “biodiversity index” is too broad, whereas “Shannon’s biodiversity index” is appropriate. 
-->

Not applicable

## Analysis Plan

<!-- 
You may describe one or more confirmatory analysis in this preregistration. Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.
A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis. You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required. 
-->

I will build a network of the wikilinks for each group, where: 
- nodes = biographical figure/subject of the article 
- edges = wikilinks between articles; direction of edge showing what page the link is from. 

Then I will analyze the density and modularity of each network and compare them to each other and some random networks that preserve key features of the original networks (number of nodes and edges, etc)

### 19. Statistical models

<!-- 
What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions, subgroup analyses, pairwise or complex contrasts, or follow-up tests from omnibus tests. If you plan on using any positive controls, negative controls, or manipulation checks you may mention that here. Remember that any test not included here must be noted as an exploratory test in your final article. 
Example:  We will use a one-way between subjects ANOVA to analyze our results. The manipulated, categorical independent variable is 'sugar' whereas the dependent variable is our taste index. 
More information: This is perhaps the most important and most complicated question within the preregistration. As with all of the other questions, the key is to provide a specific recipe for analyzing the collected data. Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user? Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test. See the following examples: 
If someone specifies a 2x3 ANOVA with both factors within subjects, there is still flexibility with the various types of ANOVAs that could be run. Either a repeated measures ANOVA (RMANOVA) or a multivariate ANOVA (MANOVA) could be used for that design, which are two different tests. 
If you are going to perform a sequential analysis and check after 50, 100, and 150 samples, you must also specify the p-values you’ll test against at those three points.
-->

Describe your planned statistical model(s) here. 

### 20. Transformations 

<!-- 
If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process.
Example: The “Effect of sugar on brownie tastiness” does not require any additional transformations. However, if it were using a regression analysis and each level of sweet had been categorically described (e.g. not sweet, somewhat sweet, sweet, and very sweet), ‘sweet’ could be dummy coded with ‘not sweet’ as the reference category. 
More information: If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g. dummy coding, summation coding, etc.) and what the reference category will be. 
-->

Not applicable. 

### 21. Inference criteria 

<!-- 
What criteria will you use to make inferences? Please describe the information youÍll use (e.g. p-values, bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?
Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct. The post-hoc Tukey-Kramer test adjusts for multiple comparisons. 
More information: P-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields. Bayesian analyses should specify a Bayes factor or a credible interval. If you are selecting models, then how will you determine the relative quality of each? In regards to multiple comparisons, this is a question with few “wrong” answers. In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate. One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.
-->

Describe your inference criteria here or state not applicable.

### 22. Data exclusion 

<!-- 
How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled? Will you use any awareness check?
Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices. Outliers will be included in the analysis. 
More information: Any rule for excluding a particular set of data is acceptable. One may describe rules for excluding a participant or for identifying outlier data.
-->

Observations will be exluded if they: 
 1) Are not a biographical Wikipedia article (ex: objects, concepts, places and lists are frequently the subject of Wikipedia articles and could have been edited by the movements. However the primary focus of the movements are editing biographical pages of women so they will not be examined here)
 2) I'm only looking at wikilinks to other biographies in my dataset, for example, if Frida Kahlo's Wikipedia article (which is quite robust already) is not edited by the Art+Feminism, I won't look at Wikilinks to her. 

### 23. Missing data

<!-- 
How will you deal with incomplete or missing data?
Example: If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis.
More information: Any relevant explanation is acceptable. As a final reminder, remember that the final analysis must follow the specified plan, and deviations must be either strongly justified or included as a separate, exploratory analysis. 
--> 

Not applicable. 

### 24. Exploratory analysis

<!-- 
If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time. 
Example: We expect that certain demographic traits may be related to taste preferences. Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences.
-->

Enter any plans for exploratory data analysis here or state not applicable.

## Other 

### 25. Other 

<!-- 
If there is any additional information that you feel needs to be included in your preregistration, please enter it here. Literature cited, disclosures of any related work such as replications or work that uses the same data, or other context that will be helpful for future readers would be appropriate here. 
-->

Enter any additional information not covered by other sections, or state not applicable. 

## References 

Enter any references used throughout the text here.
